On Verification Patterns for Low-Level Systems via Modal Abstractions

### 2025-09-02 paper.tex
+
plos files

%\documentclass[a4paper,UKenglish]{lipics-v2016}
% For two-column layout for PPoPP, change 'acmsmall' to 'sigplan'.  Probably also turn on the
% 'review' option, and the 'anonymous' option if it's DBR
\documentclass[runningheads]{llncs}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"
\usepackage[export]{adjustbox}

\usepackage{booktabs}
\usepackage{multirow}
 \usepackage{proof}
 \usepackage{array}
 \usepackage{iris}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}

\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
%\usepackage{t1enc}
%\usepackage[strings]{underscore}
%%%%%\usepackage{geometry}
\usepackage{wrapfig}
\usepackage[rawfloats=true]{floatrow} 
\restylefloat{figure}    
\DeclareMathSizes{4}{4}{4}{4}
\usepackage{varwidth}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage[fleqn]{amsmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xspace}
\usepackage{listings}
\usepackage{comment}
\usepackage{longtable}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage[toc,page]{appendix}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{graphics,graphicx}
\usepackage{mathpartir}
\usepackage{array}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc, shapes, backgrounds}
\usepackage{verbatim}
\usepackage{tikz-qtree}
\usepackage{pgfplots}
\usepackage{caption,capt-of}
\usepackage{color}
\usepackage{soul}
\setul{1ex}{0.8ex}
\definecolor{orange}{rgb}{1,0.5,0}
\setulcolor{orange}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{afterpage}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{rotating}

%%sequeezeeee
\addtolength{\textfloatsep}{-10pt}
\addtolength{\dbltextfloatsep}{-10pt}

\newcommand{\ptree}{\text{\faSitemap}@[\ell]}
\newcommand{\mtree}{\varupphi\text{\faSitemap}@[\ell]^{\Pi}_{\pi}(\sigma)}
\newcommand{\oprtree}[4]{#3\;\text{\faSitemap}@[\textsf{#1_{#2}}]^{\Pi}_{\pi}(#4)}

\newcommand{\osubtree}[4]{#2\;\text{\faSitemap}@[\textsf{node}_{#1}]^{\Pi}_{\pi}(#3_#4)}
\newcommand{\otree}[3]{#2\;\text{\faSitemap}@[\textsf{node}_{#1}]^{\Pi}_{\pi}(#3)}
\newcommand{\oltree}[3]{#2\;\text{\faSitemap}@[#1]^{\Pi}_{\pi}(#3)}

\newcommand{\defeq}{\mathbin{\stackrel{\text{def}}{=}}}
% some stuff for prettier proof outlines
\newcommand{\havoc}{\textsf{havoc}}
\newcommand{\specline}[1]{{\color{blue}\left\{#1\right\}}}
\newcommand{\assertion}[1]{\textsf{assert} {\color{red}\left\{#1\right\}}}
\newcommand{\proofstepnr}[5][1pt/3pt]{\small \left.
\begin{array}{l}
\hdashline[#1]
\ensuremath{\specline{#2}}\\
\begin{array}{l}
#3
\end{array}\\

\ensuremath{\specline{#5}}\\
\hdashline[1pt/3pt]
\end{array}
\color{green}\right)\hspace{-6pt}{\color{green}-}
\begin{array}{@{}l@{}}
#4
\end{array}
}
\newcommand{\proofoutstepnr}[5][1pt/3pt]{\small \left.
\begin{array}{@{}l@{}}
\hdashline[#1]
\ensuremath{\specline{#2}}\\
\begin{array}{@{\;\;\;}l}
#3
\end{array}\\
\ensuremath{\specline{#5}}\\
\hdashline[1pt/3pt]
\end{array}
\color{green}\right)\hspace{-6pt}{\color{green}-}
\begin{array}{@{}l@{}}
#4
\end{array}
}
% \proofoutstep[dash stuff]{pre}{C}{rule}{post}
\newcommand{\proofoutstep}[5][1pt/3pt]{
\proofoutstepnr[#1]{#2}
{#3}
{\rotatebox[origin=c]{90}{$\begin{array}{@{}c@{}}{}#4\end{array}$}}
{#5}
}
\newcommand{\sepimp}{\mathrel{-\mkern-6mu*}}
\newcommand{\NULL}{\texttt{NULL}}
\newcommand{\NEW}{\texttt{new}}
\newcommand{\SKIP}{\texttt{skip}}
\newcommand{\RESULT}{\texttt{result}}
\newcommand{\class}{\texttt{class}}
\newcommand{\where}{\texttt{where}}
\newcommand{\readable}{\texttt{readable}}
\newcommand{\writable}{\texttt{writable}}
\newcommand{\isolated}{\texttt{isolated}}
\newcommand{\immutable}{\texttt{immutable}}
\newcommand{\consume}[1]{\texttt{consume}(#1)}
\newcommand{\consumeiso}[1]{\mathsf{RemIso}(#1)}
\newcommand{\INT}{\texttt{int}}
\newcommand{\bool}{\texttt{bool}}
\newcommand{\this}{\texttt{this}}
\newcommand{\immutdecl}[1]{\mathsf{ImmutableDeclared}(#1)}
\newcommand{\IsoOrImm}{\textsf{IsoOrImm}}
\newcommand{\NonWrit}{\textsf{NoWrit}}
\newcommand{\db}[1]{\llbracket#1\rrbracket}
\newcommand{\nil}{\textsf{null}}
\newcommand{\atom}{\textsf{atom} \mapsto \mstatename \mapsto \mstatename}
\newcommand{\loc}{\textsf{Loc}}
\newcommand{\val}{\textsf{Val}}
\newcommand{\mstatename}{\textsf{MState}}
\newcommand{\superset}{\mathcal{P}}
\newcommand{\mstatedecl}{\sigma \in \mstatename \overset{def}{=} s \times h \times l \times rt \times R \times B  \times F }
\newcommand{\stack}{s \in \var \times \tid \rightharpoonup \loc}
\newcommand{\heap}{h \in \loc \times \fname \rightharpoonup \val}
\newcommand{\wlock}{l \in \tid \uplus \textsf{unlocked}}
\newcommand{\rlock}{R \in \superset(\tid)}
\newcommand{\fset}{F : \loc \mapsto \superset(\tid) }
\newcommand{\atomeval}{\db{-}:\atom}
\newcommand{\rcuwrite}{\textsf{RCUWrite} \text{ x.f as y in }\, \{ C \}}
\newcommand{\rcuread}{\textsf{RCURead} \text{ x.f as y in }\, \{ C \}}
  \newcommand{\desugarread}{ \rcuread \overset{\Delta}{=} \texttt{\textsf{ReadBegin}}; y = x.f;\{C'\}  ;\textsf{ReadEnd} }
  \newcommand{\desugarwrite}{\rcuwrite \overset{\Delta}{=} \texttt{\textsf{WriteBegin}} ; y = x.f ; \{C'\}  ;\textsf{WriteEnd}}
    \newcommand{\desugarsync}{\textsf{Sync} \overset{\Delta}{=} \texttt{\textsf{SyncStart};\textsf{SyncStop}}}
  %\newcommand{\boundpath}{\bar f_{i}^{k} = \forall_{k \in \mathbb{N},i \in \fnameenum} \ldotp  \underbrace{f_{i}^{0} \ldots f_{i}^{k}}_\text{$\mid$ $f_{i}^{0}$ \ldots $f_{i}^{k}$ $\mid$ = k} }
\newcommand{\subt}{\prec:}
%typing rules
 \newcommand{\fname}{\textsf{FName}}
\newcommand{\fmname}{\textsf{FMap}}
\newcommand{\uiglobal}{\textsf{UIGlobal}}
\newcommand{\udef}{\textsf{undef}}
\newcommand{\unlinked}{\textsf{unlinked}}
\newcommand{\fresh}{\textsf{fresh}}
\newcommand{\var}{\textsf{Var}}
\newcommand{\tid}{\textsf{TID}}

\newcommand{\fmapfieldemp}{\N_{f,\emptyset} = \N \setminus \{f \rightharpoonup \_ \}}
\newcommand{\fmapname}{\N = \{ f_0|\ldots|f_n\rightharpoonup  \{y\} \mid f_{i} \in \fname \land \; 0\leq i\leq n  \land \; (y \in \var \lor y \in \{null\}) \}}
\newcommand{\fmapextend}{  \N(f\rightharpoonup x \setminus y) = \N \setminus \{f \rightharpoonup x\} \cup \{f \rightharpoonup y\} }
\newcommand{\fmapextendn}{  \N(\cup_{f\rightharpoonup y}) = \N \cup \{f \rightharpoonup y\} }
\newcommand{\fmapdiff}{\N(\setminus_{f\rightharpoonup y}) = \N - \{f\rightharpoonup y\}}
\newcommand{\fmapwithf}{\N([f\rightharpoonup  y]) = \N \text{   where  } f \rightharpoonup y \in \N }
\newcommand{\fmapempty}{\N_{\emptyset} =  \{ \}}
\newcommand{\codom}{\cod(\N)=\dom(\Gamma)}
\newcommand{\cod}{\texttt{cod}}
\newcommand{\dom}{\texttt{dom}}
%\newcommand{\types}{\tau ::= \textsf{rcu} | \textsf{normal}}

\newcommand{\rpth}{f \in \textsf{FName} 
     \left\{\begin{array}{cl}
     \epsilon &    \\
     f  &  f \in \fname\\
   f_1 | \ldots | f_n &\forall_{1 \leq i \leq n} \ldotp f_i \in \fname 
     \end{array}\right\}
     \quad \text{  where } \textsf{FType(f) = \textsf{RCU}}
}
\newcommand{\rextendswith}{\rho^{k}[i] \mapsto f_i \text{  where  } \forall_{0\leq i \leq k} \ldotp f_i \in \fname }
\newcommand{\extendswith}{\rho[i] \mapsto \rho_{i}^{k} \text{  where  } \forall_{0\leq i \leq n} \ldotp \rho_i^{k} \in \textsf{RelativePath}}

\newcommand{\pth}{\rho \in \textsf{Path}  \qquad \rho ::= \rho_1 \ldots\rho_n  \text{   where  } \forall_{0\leq i \leq n}\ldotp \rho_i \in \textsf{RelativePath} \text{ or } \rho_i \in \textsf{ConcretePath}}
\newcommand{\cpath}{\forall_{0 \leq i \leq n} \ldotp f_i \in \mathsf{FName} \land l_i \in \textsf{Label} \land \exists_{k\geq0} \ldotp f_i^{l_i} = \overbrace{f_i\ldots f_i}^{k} \land (\forall_{0\leq j \leq n} \ldotp j\neq i \implies l_i \neq l_j) }

\newcommand{\rpath}{\rho \in \textsf{RelativePath} \quad \rho = (f)^{*} \text{   where  } f \in \textsf{FName} \text{  and  } \exists_{k>=0} \ldotp (f)^{*} = \overbrace{f\ldots f}^\text{k} }
\newcommand{\falt}{f \in \textsf{AlternatingFName} = f_1 | f_2 | \ldots | f_{n-1} | f_n \text{  where  } \forall_{0\leq i \leq n}\ldotp f_i \in \textsf{FName} }

\newcommand{\lenmap}{\mathcal{L} \in \textsf{LPath} : \rho \mapsto \mathbb{N}}
\newcommand{\etadecl}{\eta = \{f \mapsto y \mid f \in \fname \land y\in \var \}  }
\newcommand{\rcunfd}{\textsf{rcuFresh} \,  \N}
\newcommand{\rcunfdecl}{x : \textsf{rcuFresh} \;\; \N }
\newcommand{\rcunf}[3]{#1 : \textsf{rcuFresh} \;\; \N(\cup_{ #2 \rightharpoonup #3}) } %x, f , y
\newcommand{\rcuf}[1]{#1 : \textsf{rcuFresh} \;\;\N } %x, f , y
\newcommand{\rcunextfresh}[1]{\textsf{rcuFresh} \;\; \N #1 }
\newcommand{\ftypedecl}{\textsf{FType} : \fname \mapsto \tau}
\newcommand{\ftype}[2]{\textsf{FType}(f_{#1}) \mapsto \textsf{#2}}
%%%
\newcommand{\typedepthdecl}{\textsf{TypeDepth}(x:\text{T}) =  \mid\rho\mid \;\; \texttt{where T} = \textsf{rcuItr} \underset{y}{\mid} \rho \,\, \N }
%%%
\newcommand{\rcuonly}{\textsf{RCUOnly}(x) \overset{\texttt{def}}{=} x:T \text{ where } T = \textsf{rcuItr}\_}
\newcommand{\rcumodonlydecl}{\textsf{RCUModifiedOnly}(C) \overset{\texttt{def}}{=} \forall_{x \in \textsf{Modifies}(C)}\ldotp \textsf{RcuOnly}(x) }
\newcommand{\rcufilterb}{\textsf{RemRcu} : \Gamma \mapsto \Gamma}
\newcommand{\rcufilterr}[1]{\textsf{RemRcu} ( #1 ) = \texttt{filter} \, ( \lambda x \ldotp x \neq \textsf{rcuItr \_ } ) \,  #1 }
\newcommand{\rcufiltera}[1]{\textsf{RemRcu} ( #1 ) }
%%%Alias
\newcommand{\aliaswith}[2]{#1 \in \textsf{AliasWith}(#2)}
\newcommand{\aliaswithdecl}{\textsf{AliasWith}(x) = \{y \mid y:\textsf{rcuItr}\underset{r',k'}{\mid} \rho' \;\; \N' \land \rho = \rho' \land \N = \N' \}  \texttt{  where  }  \rcuitrT{x}{r}{k}{kk}{\_} }
%%%Framing Type Contexts
    \newcommand{\wellframed}{
      \mathsf{WellFramed}(\Gamma,\Delta)\overset{def}{=}
      \left\{\begin{array}{l}

        \forall_{z\in dom(\Gamma),f,\rho,y }\ldotp                           z\notin dom(\Delta) \land            z:\textsf{rcuItr}\,\rho\,\N([f\rightharpoonup y]) \implies \\
                      \left\{ 
	              \begin{array}{l}
                        y\notin dom(\Delta) \land y\in dom(\Gamma) \land \forall_{n\in dom(\Delta),\rho',f',m}\ldotp n\notin dom(\Gamma) \land 	\\
            \left\{
            \begin{array}{l}
              n:\textsf{rcuItr}\,\rho'\,\N([f'\rightharpoonup m]) \implies \\
              \left\{\begin{array}{l}
              m \notin dom(\Gamma) \land \\
              m \in dom(\Delta) \land
              \rho \neq \rho'                    
              \end{array} \right\}
            \end{array}\right\}
     \end{array}\right\}
         \end{array}\right.

}

%%%Framing Type Contexts ends
\newcommand{\deltaepsilon}{\Delta >= 0 \qquad 0\leq \epsilon \leq \Delta }
\newcommand{\reduce}[2]{\textsf{InReduction}(#1,#2) = \{ \Gamma' \mid  \Gamma' \preceq_{\varepsilon} \Gamma \} }
\newcommand{\rename}[2]{\textsf{ContextRename}(#1,#2) = #2 \mapsto #1 }
%%Sep RCU
\newcommand{\seprcu}[4]{\textsf{SepLoop}(#1,#2,#3,#4) \overset{\texttt{def}}{=} \text{dom}(#1)\cap \text{dom}(#2) = \emptyset \, \land \, #1\uplus#2= #4 \, \land \, \textsf{RcuModifiedOnly}(#2,#3)}
\newcommand{\seprcud}[4]{\textsf{SepLoop}(#1,#2,#3,#4)}
%%
\newcommand{\seprcub}[5]{\textsf{SepBranch}(#1,#2,#3,#4,#5) \overset{\texttt{def}}{=}
   \left\{\begin{array}{cl}
  \text{dom}(#2)\cap \text{dom}(#3) = \emptyset \, \land \, #2\uplus#3=#1 \land \\
  \textsf{RcuModifiedOnly}(#2,#4) \,\land\, \textsf{RcuModifiedOnly}(#2,#5)\,\land \\

 \end{array}\right\}
}
\newcommand{\seprcubd}[5]{\textsf{SepBranch}(#1,#2,#3,#4,#5)}
%%
\newcommand{\precgamma}[2]{#1  \preceq #2 \overset{\texttt{def}}{=} \forall_{(x)\in #1}\ldotp x \in #2 \implies  #1 \preceq_{x} #2}
%%%if branches
\newcommand{\iffree}{\textsf{if}(\text{e})\{\text{C}\}}
\newcommand{\ifelse}{\textsf{if}(\text{e})\{\text{C}_1\}\textsf{else}\{\text{C}_2\}}
%%var  root,k  , k+1 mappedvar
\newcommand{\rcuitertype}[4]{\textsf{rcuItr}(#1,#2)\;#3\;#4}
\newcommand{\rcuit}[4]{#1:\textsf{rcuItr}\;\; #3 \;\; #4 }
\newcommand{\rcuitrT}[5]{#1:\textsf{rcuItr}\;\; \rho \;\; \N }
\newcommand{\rcuitrn}[5]{#1:\textsf{rcuItr}\;\; \rho \, f \;\; \N }
\newcommand{\rcuitr}[5]{#1:\textsf{rcuItr}\;\; \rho \;\; \N[f  \rightharpoonup #5] }
\newcommand{\rcustack}[2]{#1 : \textsf{rcuItr}\underset{#2}{\mid}}
\newcommand{\afree}[1]{\textsf{asyncDelayedFree}(#1)}
\newcommand{\allocate}{\textsf{asyncDelayedFree}}
\newcommand{\typelocal}{\tau_{local}}
\newcommand{\typeglobal}{\tau_{global}::=\textsf{rcuRoot}  }
\newcommand{\rcutypes}{ \typelocal ::=   \textsf{undef} \mid \textsf{rcuItr} \,\, \rho \,\, \N \mid \rcunfd \mid \textsf{unlinked}  \mid \textsf{freeable}}
\newcommand{\typelocalmap}{\textsf{TypeLocal} : \var \mapsto \typelocal}
\newcommand{\command}[1]{\db{#1} \mstate \commandeq}
\newcommand{\commandm}[2]{\db{#1} #2 \commandeq}

\newcommand{\mstate}{(s,h,l,R,F)}
\newcommand{\commandeq}{\;\;\Downarrow_{\mathrm{tid}}\;\;\overset{\Delta}{=}}
\newcommand{\op}[2]{\begin{array}{rll}\command{#1} & #2\end{array}}
\newcommand{\opm}[3]{\begin{array}{rll}\commandm{#1}{#2} & #3\end{array}}
%%%
\newcommand{\return}[1]{\mathsf{return~\mathit{#1}}}
\newcommand{\bind}[2]{\mathsf{Bind}(#1;#2)}
\newcommand{\result}[1]{\mathsf{y = \mathsf{result}}}
\newcommand{\mbody}[2]{\mathsf{mbody}(#1,#2)}
\newcommand{\pre}{\textsf{pre}}
\newcommand{\assume}[1]{\textsf{assume}(#1)}
\newcommand{\lift}[1]{\lceil #1\rceil}
\newcommand{\erase}[1]{\lfloor #1\rfloor}
%%%
\newcommand{\M}{\ensuremath{\mathcal{M}}}
\newcommand{\s}{\ensuremath{\mathcal{S}}}
\newcommand{\R}{\ensuremath{\mathcal{R}}}
\newcommand{\N}{\ensuremath{\mathcal{N}}}
\newcommand{\condexpr}{e \in \textsf{CondExpr}}
%function definitions for paths

\newcommand{\lengthofpath}{$\mid \rho\mid \;=\;
  \begin{cases}
      0+ \mid \rho'\mid &  \rho = \rho_{i}^{k}\rho' \text{   where  } 0\leq i  \text{   and   } \rho_{i}^{k} = \epsilon \\
         k + \mid \rho'\mid & \rho = \rho_{i}^{k}\rho' \text{   where  } 0\leq i
  \end{cases}$

}
%%\textsf{Stabilize}(\Gamma,e) = \forall x \in \N[\fname] \ldotp \exists_{f_1,f_2 \in \fname}\ldotp \N[f_1] =  \N[f_2] \implies \N[f_1,f^{*}] \land \N[f_2,f^{*}]

\newcommand{\stabilizenext}{\textsf{StabilizeNext}(a,b,f)}
\newcommand{\stabilizepath}{\textsf{StabilzePath}(b,f,k)}
\newcommand{\stabilizecontext}{\textsf{StabilizeContext}(\Gamma,e) =
    \left\{\begin{array}{cl}
    e \in \textsf{PointsToExpr} \land
    \exists_{a,b,f}\ldotp  (a,b,f) = \textsf{PointsToExprMap}(e) \land \\
  \pi_{\N}(a) = \textsf{StabilizeNextMap}(a,b,f) \land \\
  \pi_{\rho}(b) = \textsf{StabilizePath}(b,f, \mid \pi_{\rho}(b)\mid ) \land\\
  \forall_{c \in \Gamma \land \textsf{TypeDepth}(c) >= \textsf{TypeDepth}(b)} \ldotp \pi_{\rho}(c) = \textsf{StabilizePath}(c,f,\mid\pi_{\rho}(c)\mid)
  \end{array}\right\}
}
%%%frame branch
\newcommand{\alternatingvars}[1]{\textsf{AbstractVars}(#1)}
\newcommand{\alternatingvarsdecl}{\textsf{AbstractVars}(\Gamma) \;=\; \{ x,y \mid  (x,y)\in \textsf{AbstractPairs}(\Gamma)\}}
\newcommand{\alternatetype}{ \text{x:}\textsf{rcuItr}\;\; \rho \;\; \N[f^{*}\mapsto y] \qquad   \text{y:}\textsf{rcuItr}\;\; \rho.\rho^{k} \;\; \N \text{    where    } \rho^{k}[k]=f^{*}}
\newcommand{\alternatingpath}[1]{f^{*} \; = \; f_1 \mid f_2  \; \text{where} \;  (f=f_1) \;\oplus \; ( f=f_2 )  }
\newcommand{\alternatingpathsdecl}[1]{\textsf{AbstractPairs}(#1) = \; \{ (\text{x},\text{y}) \mid \text{x} \in #1 \land \text{y} \in #1\}}
\newcommand{\alternatingpaths}[1]{\textsf{AbstractPairs}(#1)}
\newcommand{\pointstotuple}{\textsf{PointsToTuple}}
\newcommand{\pointstoexpr}{\textsf{PointsToExpr} = \{ x.f==y  \in \textsf{Expr} \mid \text{x} \in \var \; \land \; \text{y} \in \var \; \land \; f \in \fname \}}
\newcommand{\pointstopair}[1]{\textsf{PointsTo}(\text{#1})}
\newcommand{\projectfieldecl}{\pi_{f} : (\text{x},\text{y},f) \mapsto f}
\newcommand{\projectfield}[1]{\pi_{f}(#1)}
\newcommand{\projectpairdecl}{\pi_{\var} :(\text{x},\text{y},f) \mapsto (\text{x},\text{y})}
\newcommand{\projectpair}[1]{\pi_{\var}(#1)} % tuple,f.
\newcommand{\pointstoexprdecl}{\textsf{PointsToExpr} = \{e \mid  e = (a.f == b) \land \condexpr \land a,b \in \var \land f \in \fname  \} }
\newcommand{\pointstostmtdecl}{\textsf{PointsToExprMap}: \textsf{PointsToExpr}\mapsto \var \times \var \times \fname}
\newcommand{\pointstostmt}[1]{\textsf{PointsToExprMap}(#1) }
\newcommand{\freductionindexdecl}{\textsf{FieldReductionIndex}(\text{C},\text{x},\text{y},\text{irdc})\; = \;
  \left\{\begin{array}{cl}
    \forall_{0 \leq  i \leq n} \ldotp &  (x',y',f')_{i}  \in \pointstostmt{C} \land \\
    &(\text{x},\text{y})= \projectpair{(\text{x}',\text{y}',f')_{i}} \implies\\
    & \left\{\begin{array}{cl}
    \exists_{ firdc} \ldotp  & firdc \leq i \land  (firdc = 0 \implies firdc=irdc) \land \\
     & \left\{\begin{array}{cl}
    \forall_{0 \leq none \le firdc} \ldotp & (\text{x},\text{y}) \neq \projectpair{(\text{x}',\text{y}',f')_{none})}  \land \\
    &  firdc = \text{irdc}
      \end{array}\right\}
    \end{array}\right\}
  \end{array}\right\}
}

\newcommand{\projectsharpdecl}{\Pi_{\varphi_{e}}(f^{*}) \mapsto f_1 \qquad \Pi_{\lnot\varphi_{e}}(f^{*}) \mapsto f_2 }
\newcommand{\projectsharpdeclback}{\Pi(\varphi_{e})\mapsto e}

\newcommand{\frenamefielddecl}{\textsf{FieldRename}(\text{x},f,f')  \; = \; \text{x:T}[f/f'] }

\newcommand{\freductiondecl}{\textsf{FieldReduction}(\Gamma,\varphi_{e}) \; = \;
\left\{\begin{array}{cl}
  \textsf{FieldRename}(\text{x},f^{*},\Pi_{\varphi_{e}}(f^{*})),
  \textsf{FieldRename}(\text{y},f^{*},\Pi_{\varphi_{e}}(f^{*})) \mid (\text{x},\text{y}) =\projectpair{\pointstostmt{\Pi(\varphi_{e})}}
\end{array}\right\}
}

\newcommand{\freductiondeclneq}{\textsf{FieldReduction}(\Gamma,\lnot\varphi_{e}) \; = \;
\left\{\begin{array}{cl}
  \textsf{FieldRename}(\text{x},f^{*},\Pi_{\lnot\varphi_{e}}(f^{*})),
  \textsf{FieldRename}(\text{y},f^{*},\Pi_{\lnot\varphi_{e}}(f^{*})) \mid (\text{x},\text{y}) = \projectpair{\pointstostmt{\Pi(\varphi_{e})}}
\end{array}\right\}
  }

>>>>

%%
%% This is file `sample-sigconf-authordraft.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,authordraft')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf-authordraft.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,10pt]{acmart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}
%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation email}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/2018/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
 \usepackage{proof}
\usepackage{array}
\usepackage{iris}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}
% Useful macros from Isaac Oscar Gariano: a very simple library for author-specific change notations:
%  After calling \newAuthor{<name>}{<colour>}
% You can use \<name>{<text>} to add a comment
% Or \<name>A{<text>} to  write stuff in your colour (to denote additional text)
% Or \<name>B{<text>} is similar, but changes the background (to highlight stuff?)
% I may add more commands later
% (there's a 'changes' package with similar functionality, but it has a habit of breaking when you use it with  the Define environment)
\newcommand\newAuthor[2]{%
        \ExpandArgs{c}\newcommand{#1}[1]{\todo[color=#2!10, bordercolor=#2, inline]{\textbf{#1:}~##1}}
	\ExpandArgs{c}\newcommand{#1A}[1]{\textcolor{#2}{##1}}
        \ExpandArgs{c}\newcommand{#1B}[1]{\colorbox{#2!30}{\textcolor{black}{##1}}}}
\newtheorem*{remark}{Remark}
\newcommand{\loc}{\textsf{Loc}}
\newcommand{\sepimp}{\mathrel{-\mkern-6mu*}}
\newcommand{\blackdiamond}{\rotatebox[origin=c]{45}{$\vcenter{\hbox{$\scriptscriptstyle\blacksquare$}}$}}

\newAuthor{Ismail}{blue}
\newAuthor{Colin}{cyan}

%% The "title" command has an optional parameter,
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{On Verification Patterns for Low-Level Systems via Modal Abstractions}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
% Commentout
%\author{Ben Trovato}
%\authornote{Both authors contributed equally to this research.}
%\email{trovato@corporation.com}
%\orcid{1234-5678-9012}
%\author{G.K.M. Tobin}
%\authornotemark[1]
%\email{webmaster@marysville-ohio.com}
%\affiliation{%
 % \institution{Institute for Clarity in Documentation}
 % \city{Dublin}
 % \state{Ohio}
 % \country{USA}
%}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Although they differ in the functionality they offer, low-level systems exhibit certain patterns of design and utilization of computing resources.
